---
title: "Introduction to ryx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ryx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryx)
```

## Using ryx() without specifying comparison Variables (x) for the selected variable (y) 
```{r}
library(MASS)
object <- ryx(Boston, y="medv")
```

# Now let's get a summary of the correlations between medv and all the other variables
```{r}
summary(object)
```

# Now let's print out all of the correlations between medv and all the other variables

```{r}
print(object)
```

# Now let's plot all of the correlations between medv and all the other variables
```{r}
plot(object)
```

## Using ryx() specifying comparison variables (x) for the selected variable (y)

```{r}
data(mtcars)
object2 <- ryx(mtcars, y = "mpg", x = c("qsec","gear","carb", "cyl"))
```

# Now let's get a summary of the correlations between mpg and all the specified variables
```{r}
summary(object2)
```

# Now let's print out all of the correlations between mpg and all the specified variables

```{r}
print(object2)
```

# Now let's plot all of the correlations between mpg and all the specified variables
```{r}
plot(object2)
```
